### 2017-01-08 README.Rmd
update README

There are two main commands in the `visdat` package: 
- `vis_dat()` 
- `vis_miss()`

@@

At the moment `vis_guess` is very slow. Please take this into consideration when you are using it on data with more than 1000 rows. We're looking into ways of making it faster, potentially using methods from the `parallel` package, or extending the c++ code from `readr:::collectorGuess`.

@@

This is also just brand new under development, but should prove interesting once I fix up the legend, etc.

```{r eval = FALSE, echo = TRUE}

>>>>

There are two main commands in the `visdat` package:

- `vis_dat()` 
- `vis_miss()`

@@

At the moment `vis_guess` is very slow. Please take this into consideration when you are using it on data with more than 1000 rows. We're looking into ways of making it faster, potentially using methods from the `parallel` package, or extending the c++ code from `readr::parse_guess`.

@@

This is also under development, and still needs some more work on the legend, etc.

```{r vis-miss-ly}
